---
title: "STAT 231: Problem Set 1B"
author: "Brandon Kwon"
date: "due by 5 PM on Friday, February 26"
output: pdf_document
---

Series B homework assignments are designed to help you further ingest and practice the material covered in class over the past week(s).  You are encouraged to work with other students, but all code must be written by you and you must indicate below who you discussed the assignment with (if anyone).  

Steps to proceed:

\begin{enumerate}
\item In RStudio, go to File > Open Project, navigate to the folder with the course-content repo, select the course-content project (course-content.Rproj), and click "Open" 
\item Pull the course-content repo (e.g. using the blue-ish down arrow in the Git tab in upper right window)
\item Copy ps1B.Rmd from the course repo to your repo (see page 6 of the GitHub Classroom Guide for Stat231 if needed)
\item Close the course-content repo project in RStudio
\item Open YOUR repo project in RStudio
\item In the ps1B.Rmd file in YOUR repo, replace "YOUR NAME HERE" with your name
\item Add in your responses, committing and pushing to YOUR repo in appropriate places along the way
\item Run "Knit PDF" 
\item Upload the pdf to Gradescope.  Don't forget to select which of your pages are associated with each problem.  \textit{You will not get credit for work on unassigned pages (e.g., if you only selected the first page but your solution spans two pages, you would lose points for any part on the second page that the grader can't see).} 
\end{enumerate}

```{r, setup, include=FALSE}
# Load packages here 
library(mdsr)   
library(tidyverse)

knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small",   # slightly smaller font for code
  message=FALSE)   
```

\newpage 

# If you discussed this assignment with any of your peers, please list who here:

> ANSWER:



\newpage
# MDSR Exercise 2.5 (modified)

Consider the data graphic for Career Paths at Williams College at: https://web.williams.edu/Mathematics/devadoss/careerpath.html.  Focus on the graphic under the "Major-Career" tab.

a. What story does the data graphic tell?  What is the main message that you take away from it?

> ANSWER: The data graphic displays the relationship between major and possible career paths through the utilization of arcs that connect parts of the circle to other parts of the circle.  As a result, I believe the story the data graphic is trying to convey is one that emphasizes the fact that the type of major one pursues in college is very much related to the career pathway that he/she chooses in the future.  We can infer this conclusion by using our prior knowledge about the careers and the main focus of each major in the data graphic.  However, I also believe that the data graphic is also trying to convey that there is no one main path that a student can take in order to pursue a specific career.  One can major in practically anything and still arrive at the same destination as another student who majors in something completely different.

b. Can the data graphic be described in terms of the taxonomy presented in this chapter?  If so, list the visual cues, coordinate system, and scale(s).  If not, describe the feature of this data graphic that lies outside of that taxonomy.

> ANSWER: The data graphic can partially be described in terms of the taxonomy presented in this chapter.  In terms of visual cues, I see that position, length, direction, and color contribute to this representation greatly.  Position is significant in that each part (whether major or career) is placed in a piece of the circle in a way that allows the viewer to make connections easily.  Length is also important because each arc has different lengths as to allow the viewer to make better comparisons in terms connecting a major to a specific career path.  Direction plays a role not necessarily as an indicator of "slope" but rather as an indicator of which part connects to what as a part of the circle. (Does the arc rise upward?  Does the arc aim downward to a career path?)  I do understand that direction, however, does not contribute as much to the graphic as it would for numerical variables.  Lastly, the color is a very significant indicator of differentiating each major besides the labels themselves.
> A coordinate system is not utilized in this data graphic due to it being a circle with arcs with no designated numerical positions.
> Scale is utilized in the sense that each variable represented in this data graphic is categorical.  Type of major is categorical, as well as type of career.  There is no sense of ordering to these variables.

c. Critique and/or praise the visualization choices made by the designer.  Do they work? Are they misleading?  Thought-provoking?  Brilliant?  Are there things that you would have done differently?  Justify your response.

> ANSWER: I believe the designer did an excellent job conveying the relationship between major type and career type.  The length/direction of the arcs as well as the color of each major allowed me to make distinct connections.  The fact that I can view each career path distinctly, while also being able to see the compilation of arcs, is helpful in terms of what my purpose would be: if I wanted to view a specific career pathway and its connection with different majors, I can utilize my ability to view that career only.  If wanted a broad picture of how majors relate to career pathways in general, I have the option to view the compilation of arcs in its entirety.  One aspect I find puzzling, however, is that for some arcs, they "thin" out towards the middle.  I do not understand why the designer wanted to convey this feature, but I am interested in learning why this feature was displayed in the graphic.  If I were to change one characteristic of this graph, I would also consider utilizing different shades in allowing each career pathway to be represented more distinctly in eyes of the viewer.


\newpage
# Spot the Error (non-textbook problem)

Explain why the following command does not color the data points blue, then write down the command that will turn the points blue.

> ANSWER: The following command does not color the data points blue because 

```{r}
library(ggplot2)
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
```


\newpage
# MDSR Exercise 3.6 (modified)

Use the `MLB_teams` data in the `mdsr` package to create an informative data graphic that illustrates the relationship between winning percentage and payroll in context. What story does your graph tell?

> ANSWER:

```{r}

```


\newpage
# MDSR Exercise 3.10 (modified)

Using data from the `nasaweather` package, use the `geom_path()` function to plot the path of each tropical storm in the `storms` data table (use variables `lat` (y-axis!) and `long` (x-axis!)).  Use color to distinguish the storms from one another, and use facetting to plot each `year` in its own panel.  Remove the legend of storm names/colors by adding `scale_color_discrete(guide="none")`. 

Note: be sure you load the `nasaweather` package and use the `storms` dataset from that package!

```{r}

```


\newpage
# Calendar assignment check-in

For the calendar assignment:

- Identify what questions you are planning to focus on
- Describe two visualizations (type of plot, coordinates, visual cues, etc.) you imagine creating that help address your questions of interest 
- Describe one table (what will the rows be?  what will the columns be?) you imagine creating that helps address your questions of interest

Note that you are not wed to the ideas you record here.  The visualizations and table can change before your final submission.  But, I want to make sure your plan aligns with your questions and that you're on the right track.

> ANSWER:

 